Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets

### 2024-05-16 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[t]
    \centering
    \includegraphics[width=\linewidth]{figures/ranking.pdf}
    \caption{Visual ranking of the investigated graphs w.r.t. their model evidence, computed via thermodynamic integration. Not shown are the two graphs where the arc from \gls{lnl} III to IV was removed. Their respective model evidence fell below $-1528$ and the two graphs would appear far left in the figure. In the bottom left corner, we provide a visual reference in analogy to \cref{table:bayes_factor}: E.g., any difference in the model evidence shorter than the first of the three rulers indicates that the improvement is ``barely worth a mention''. \label{fig:ranking}}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\linewidth]{figures/ranking.pdf}
    \caption{Visual ranking of the investigated graphs w.r.t. their model evidence, computed via thermodynamic integration. Not shown are the two graphs where the arc from \gls{lnl} III to IV was removed. Their respective log model evidence differed from the base graph by more than $-19$ and the two graphs would appear far left in the figure. In the bottom left corner, we provide a visual reference in analogy to \cref{table:bayes_factor}: E.g., any difference in the model evidence shorter than the first of the three rulers indicates that the improvement is ``barely worth a mention'' Anything longer than it, but shorter than the second ruler from the top indicates a ``substantial'' improvement. \label{fig:ranking}}
\end{figure*}
